---
title: "Hello R"
author: "Rudolph Allen"
date: "Data 2401"
output: 
  html_document: 
    fig_height: 7
    highlight: espresso
    theme: journal
    toc: true
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen dataset typically contain 1428 rows and 3 columns. The variables included are

* **dataset:  Name of the dataset**
* **x:        x-values**
* **y:        y-values**

### Exercise 2
Plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```


### Exercise 3

For this part, we will plot the dataset in the star database. 
The R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient.


```{r plot-star}
star_data = datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Calculate the correlation between `x` and `y` in this dataset:
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
**The correlation in the circle data is nearly the same as the correlation in the dino data.**

### Exercise 4
For this portion of the lab, Plot y vs. x for the circle dataset.

```{r}
circle_data = datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Calculate the correlation between `x` and `y` in this dataset:

```{r}
circle_data %>%
  summarize(r = cor(x, y))

```
**The correlation in the circle data is nearly the same as the correlation in the dino data.**

### Exercise 5
Plot all datasets at once making use of facetting.

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) +   # facet the dataset variable, in 3 cols
theme(legend.position = "none")

```

Generate all the summary correlation coefficients using group_by function

```{r fig.height=9, fig.width=9}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y))

```